Progress Report

### 2023-09-12 Docs/ProgressReport.Rmd
more exploration on local GLMM unidentifiability

library(here)
library(tidyverse)
library(refund)
library(lme4)
library(ROCR)
library(GLMMadaptive)
theme_set(theme_minimal())

@@

However, this issue seems to disappear after setting nAGO=2. This argument controls the number of nodes in adaptive Gauss-Hermite quadrature approximation. This also seems to be faster and more accurate!

Reference: https://arxiv.org/pdf/2202.07864.pdf

@@

- nAGQ=0 for all bins: no warnings appeared. This is supposed to be fast but not accurate
- nAGQ=1, 2: warnings appeared in some bins.

```{r, eval=FALSE}
# re-fit local GLMM and check numeric issues
try_fit_lst<-list()
for(i in seq_along(df_bin_lst)){
  this_glm <- tryCatch({glmer(Y ~ 1 + (1|id), data = df_bin_lst[[i]], family = binomial, nAGQ=0)},
                       warning=function(w){NA})
  try_fit_lst[[i]] <- this_glm

@@

# bins where glmer returned errors
names(df_bin_lst)[is.na(try_fit_lst)]
lapply(head(try_fit_lst), summary)
```

@@

Below is the result for nAGQ = 0:

```{r}
# re-define pre_latent funciton with nAGQ = 0
pred_latent_0AGQ <- function(df){
    this_glm <- glmer(Y ~ 1 + (1|id), data = df, family = binomial, nAGQ = 0)
    eta_hat <- predict(this_glm, type = "link")
    df$eta_hat <- eta_hat
    return(df)
}

# re-fit local GLMMs
df_est_latent_0AGQ <- lapply(df_bin_lst, function(x){pred_latent_0AGQ(x)}) 
# head(df_est_latent_0AGQ[[1]])
df_est_latent_0AGQ <- bind_rows(df_est_latent_0AGQ)

@@

```{r, message=FALSE}
df %>% 
  filter(id %in% rand_id) %>%
  left_join(df_est_latent_0AGQ, by = c("id", "bin")) %>%
  mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=sind, y=eta_hat, group = id))+
  geom_point(aes(x=sind, y = Y, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  # geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
             # alpha = 0.5, linewidth = 0.5)+
  labs(x = "Time", y = "Estimated latent function (probablity scale)")
```

```{r, message=FALSE}
# overview at estimated latent function
df %>% 
  filter(id %in% rand_id) %>%
  group_by(id, bin) %>%
  summarise(num = sum(Y)) %>%
  left_join(df_est_latent_0AGQ, by = c("id", "bin")) %>%
  # mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_point(aes(x=bin, y = num, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  # geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
  #            linewidth = 0.5, alpha = 0.6)+
  labs(x = "Bin", y = "Estimated latent function/number of active minutes")
```

Obviously the lower bound of estimated latent function got a lot higher. Nothing else seems to change much.

For FPCA models below, I'll use the result from nAGQ=0 since it is free of fitting issues.

@@

```{r}
mat_est_unique <- matrix(df_est_latent_0AGQ$eta_hat, nrow=N, ncol=n_bin, byrow = F) 
# row index subject, column binned time
fpca_mod <- fpca.face(mat_est_unique, pve = 0.95, argvals = mid, var=T)

K <- ncol(fpca_mod$efunctions) # 18 eigenfunctions
```

```{r}
# population mean
plot(mid, fpca_mod$mu, type = "l", xlab = "bin", ylab = "mean")
```

```{r}
# eigenfunctions
par(mfrow=c(2,2))
plot(mid, fpca_mod$efunctions[, 1], type="l", xlab="bin", ylab="PC1")
plot(mid, fpca_mod$efunctions[, 2], type="l", xlab="bin", ylab="PC2")
plot(mid, fpca_mod$efunctions[, 3], type="l", xlab="bin", ylab="PC3")
plot(mid, fpca_mod$efunctions[, 4], type="l", xlab="bin", ylab="PC4")
```

```{r}
# covariance
heatmap(fpca_mod$VarMats[[which(unique(df_est_latent$id)==rand_id[1])]],
        Rowv = NA, Colv = NA, main = "Covariance matrix")
```

@@

```{r}
# Out-of-sample prediction
# maximum observations time: 360, 720, 1080
df_pred <- df_est_latent_0AGQ %>% filter(id %in% rand_id)
df_pred[, 'pred_t360'] <- df_pred[, 'pred_t720'] <- df_pred[, 'pred_t1080'] <- NA
score_out_mat <- array(NA, dim = c(length(rand_id), K, 3))
# dim indexes subject, eigenfunction and max obs time respectively
```

```{r, warning=FALSE}
# prediction for a single subject
for(i in rand_id){
  df_i <- df %>% filter(id==i) %>% mutate(bin=as.numeric(bin))
  # prediction
  pred_t360 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=360),
                                 fpca_fit = fpca_mod, K = K)
  pred_t720 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=720),
                                 fpca_fit = fpca_mod, K = K)
  pred_t1080 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=1080),
                                  fpca_fit = fpca_mod, K = K)
  # prediction in container
  df_pred[df_pred$id==i, 'pred_t360'] <- pred_t360$eta_pred
  df_pred[df_pred$id==i, 'pred_t720'] <- pred_t720$eta_pred
  df_pred[df_pred$id==i, 'pred_t1080'] <- pred_t1080$eta_pred
  # score in container
  # score_out_mat[i, ,1] <- pred_t360$score_out
  # score_out_mat[i, ,2] <- pred_t720$score_out
  # score_out_mat[i, ,3] <- pred_t1440$score_out
}

@@

```{r}
df_pred$pred_t360[df_pred$bin<=360] <- NA
df_pred$pred_t720[df_pred$bin<=720] <- NA
df_pred$pred_t1080[df_pred$bin<=1080] <- NA
# df_pred %>% filter(id == rand_id[1])
```

```{r, warning=FALSE}
df_pred %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id,scales = "free")
```

@@

```{r, warning=FALSE, message=FALSE, results='hide'}
df_pred2 <- df_est_latent_0AGQ %>% filter(id %in% rand_id)
df_pred2[, 'pred_t360'] <- df_pred2[, 'pred_t720'] <- df_pred2[, 'pred_t1080'] <- NA
score_out_mat2 <- array(NA, dim = c(length(rand_id), K, 3))

# unique id
# prediction for a single subject
source(here("Code/OutsampBayes.R"))

for(i in rand_id){
  df_i <- df %>% filter(id==i)

  # prediction 
  ## up to 360
  pred_t1 <- out_pred_laplace(fpca_mod, df_i %>% filter(sind<=360))
  eta_pred_t1 <- fpca_mod$mu+fpca_mod$efunctions%*%pred_t1$score_out
  df_pred2[df_pred2$id == i, 'pred_t360'] <- eta_pred_t1
  ## up to 720
  pred_t2 <- out_pred_laplace(fpca_mod, df_i %>% filter(sind<=720))
  eta_pred_t2 <- fpca_mod$mu+fpca_mod$efunctions%*%pred_t2$score_out
  df_pred2[df_pred2$id == i, 'pred_t720'] <- eta_pred_t2
  ## up to 1080
  pred_t3 <- out_pred_laplace(fpca_mod, df_i %>% filter(sind<=1080))
  eta_pred_t3 <- fpca_mod$mu+fpca_mod$efunctions%*%pred_t3$score_out
  df_pred2[df_pred2$id == i, 'pred_t1080'] <- eta_pred_t3

}
```

```{r}
df_pred2$pred_t360[df_pred2$bin<=360] <- NA
df_pred2$pred_t720[df_pred2$bin<=720] <- NA
df_pred2$pred_t1080[df_pred2$bin<=1080] <- NA
# df_pred %>% filter(id == rand_id[1])
```

```{r, warning=FALSE}
df_pred2 %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id,scales = "free")
```

>>>>

library(here)
library(tidyverse)
library(ggpubr)
library(refund)
library(lme4)
library(ROCR)
library(GLMMadaptive)
theme_set(theme_minimal())

@@

However, this issue seems to disappear after changing nAGQ. This argument controls the number of nodes in adaptive Gauss-Hermite quadrature approximation. If nAGQ=0, optimitization is done through penalized iteratively reweighted least square (PIRLS); if nAGQ=1, Laplace approximation and if nAGQ>1, adaptive Gauss-Hermite Quadrature.

Reference: https://arxiv.org/pdf/2202.07864.pdf (In fact based on this reference the recommended number of node is 0)

Another reference: https://stats.stackexchange.com/questions/544937/when-is-it-appropriate-to-set-nagq-0-in-glmer. According to this one, when setting nAGQ=0, fixed effect parameters are not optimized.

For example set nAGQ=2 for bin 465:

@@

- nAGQ=0 for all bins: no warnings appeared. This is supposed to be fast but not accurate. 
- nAGQ=1, 2, 3: warnings appeared in some bins. 
- nAGQ=5: no warnings!

```{r, eval=FALSE}
# re-fit local GLMM and check numeric issues
try_fit_lst<-list()
for(i in seq_along(df_bin_lst)){
  this_glm <- tryCatch({glmer(Y ~ 1 + (1|id), data = df_bin_lst[[i]], family = binomial, nAGQ=5)},
                       warning=function(w){NA})
  try_fit_lst[[i]] <- this_glm

@@

# bins where glmer returned errors
names(df_bin_lst)[is.na(try_fit_lst)]
glmer(Y ~ 1 + (1|id), data = df_bin_lst[['565']], family = binomial, nAGQ=3)
```

@@

Below compares the result for nAGQ = 0 and nAGQ = 5:

```{r, cache=TRUE}
# re-define pre_latent funciton with nAGQ = 0
pred_latent_0AGQ <- function(df){
    this_glm <- glmer(Y ~ 1 + (1|id), data = df, family = binomial, nAGQ = 0)
    eta_hat <- predict(this_glm, type = "link")
    df$eta_hat <- eta_hat
    return(df)
}

# re-fit local GLMMs
t1=Sys.time()
df_est_latent_0AGQ <- lapply(df_bin_lst, function(x){pred_latent_0AGQ(x)}) 
t2=Sys.time()
# head(df_est_latent_0AGQ[[1]])
df_est_latent_0AGQ <- bind_rows(df_est_latent_0AGQ)
t_0AGQ <- t2-t1

@@

```{r, cache=TRUE}
# re-define pre_latent funciton with nAGQ = 0
pred_latent_5AGQ <- function(df){
    this_glm <- glmer(Y ~ 1 + (1|id), data = df, family = binomial, nAGQ = 5)
    eta_hat <- predict(this_glm, type = "link")
    df$eta_hat <- eta_hat
    return(df)
}

# re-fit local GLMMs
t1=Sys.time()
df_est_latent_5AGQ <- lapply(df_bin_lst, function(x){pred_latent_5AGQ(x)}) 
t2=Sys.time()
# head(df_est_latent_0AGQ[[1]])
df_est_latent_5AGQ <- bind_rows(df_est_latent_5AGQ)
t_5AGQ <- t2-t1

# keep midpoint values
df_est_latent_5AGQ <- df_est_latent_5AGQ %>%
  select(-sind, -Y) %>% distinct(.)
```

- Time spent: `r t_0AGQ` for nAGQ=0, `r t_5AGQ` for nAGQ=5

```{r, message=FALSE}
ggarrange(
# nAQG=0
df %>% 
  filter(id %in% rand_id) %>%
  left_join(df_est_latent_0AGQ, by = c("id", "bin")) %>%
  mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=sind, y=eta_hat, group = id))+
  geom_point(aes(x=sind, y = Y, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  # geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
             # alpha = 0.5, linewidth = 0.5)+
  labs(x = "Time", y = "Estimated latent function (probablity scale)", title = "nAGQ=0"),
#nAGQ=5
df %>% 
  filter(id %in% rand_id) %>%
  left_join(df_est_latent_5AGQ, by = c("id", "bin")) %>%
  mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=sind, y=eta_hat, group = id))+
  geom_point(aes(x=sind, y = Y, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  # geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
             # alpha = 0.5, linewidth = 0.5)+
  labs(x = "Time", y = "Estimated latent function (probablity scale)", title = "nAGQ=5"), nrow = 1)
```

```{r, message=FALSE}
# overview at estimated latent function
ggarrange(
#nAGQ=0
df %>% 
  filter(id %in% rand_id) %>%
  group_by(id, bin) %>%
  summarise(num = sum(Y)) %>%
  left_join(df_est_latent_0AGQ, by = c("id", "bin")) %>%
  # mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_point(aes(x=bin, y = num, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  # geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
  #            linewidth = 0.5, alpha = 0.6)+
  labs(x = "Bin", y = "Estimated latent function/number of active minutes", title = "nAGQ=0")+
  ylim(-25, 10),

#nAGQ=5
df %>% 
  filter(id %in% rand_id) %>%
  group_by(id, bin) %>%
  summarise(num = sum(Y)) %>%
  left_join(df_est_latent_5AGQ, by = c("id", "bin")) %>%
  # mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_point(aes(x=bin, y = num, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  # geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
  #            linewidth = 0.5, alpha = 0.6)+
  labs(x = "Bin", y = "Estimated latent function/number of active minutes", title = "nAGQ=5")+
  ylim(-25, 10),

nrow = 1
)
```

Obviously the lower bound of estimated latent function got a lot lower using AGQ than PIRLS. Nothing else seems to change much.

@@

I would also like to compare the difference between AGQ (nAGQ=5) and PIRLS (nAGQ=0)

- AGQ has 16 eigenfunctions while PIRLS has 18

```{r}
# nAGQ=0
mat_est_unique_0AGQ <- matrix(df_est_latent_0AGQ$eta_hat, nrow=N, ncol=n_bin, byrow = F) 
# row index subject, column binned time
fpca_mod_0AGQ <- fpca.face(mat_est_unique_0AGQ, pve = 0.95, argvals = mid, var=T)

K_0AGQ <- ncol(fpca_mod_0AGQ$efunctions) # 18 eigenfunctions
```

```{r}
# nAGQ=5
mat_est_unique_5AGQ <- matrix(df_est_latent_5AGQ$eta_hat, nrow=N, ncol=n_bin, byrow = F) 
# row index subject, column binned time
fpca_mod_5AGQ <- fpca.face(mat_est_unique_5AGQ, pve = 0.95, argvals = mid, var=T)

K_5AGQ <- ncol(fpca_mod_5AGQ$efunctions) # 18 eigenfunctions
```

- Population mean function

```{r}
# population mean
par(mfrow=c(1, 2))
plot(mid, fpca_mod_0AGQ$mu, type = "l", xlab = "bin", ylab = "mean", main = "nAGQ=0", ylim = c(-25, 0))
plot(mid, fpca_mod_5AGQ$mu, type = "l", xlab = "bin", ylab = "mean", main = "nAGQ=5", ylim = c(-25, 0))
```
- PC functions
```{r, fig.height=10, fig.width=6}
# eigenfunctions
par(mfrow=c(4,2))

plot(mid, fpca_mod_0AGQ$efunctions[, 1], type="l", xlab="bin", ylab="PC1", main = "nAGQ=0")
plot(mid, fpca_mod_5AGQ$efunctions[, 1], type="l", xlab="bin", ylab="PC1", main = "nAGQ=5")

plot(mid, fpca_mod_0AGQ$efunctions[, 2], type="l", xlab="bin", ylab="PC2")
plot(mid, fpca_mod_5AGQ$efunctions[, 2], type="l", xlab="bin", ylab="PC3")

plot(mid, fpca_mod_0AGQ$efunctions[, 3], type="l", xlab="bin", ylab="PC3")
plot(mid, fpca_mod_5AGQ$efunctions[, 3], type="l", xlab="bin", ylab="PC3")

plot(mid, fpca_mod_0AGQ$efunctions[, 4], type="l", xlab="bin", ylab="PC4")
plot(mid, fpca_mod_5AGQ$efunctions[, 4], type="l", xlab="bin", ylab="PC4")
```

- Individual covariance matrix
```{r}
# covariance
heatmap(fpca_mod_0AGQ$VarMats[[which(unique(df_est_latent$id)==rand_id[1])]],
        Rowv = NA, Colv = NA, main = "nAGQ=0")
heatmap(fpca_mod_5AGQ$VarMats[[which(unique(df_est_latent$id)==rand_id[1])]],
        Rowv = NA, Colv = NA, main = "nAGQ=5")
```

@@

```{r}
# Out-of-sample prediction
# maximum observations time: 360, 720, 1080
# nAGQ=0
df_pred <- df_est_latent_0AGQ %>% filter(id %in% rand_id)
df_pred[, 'pred_t360'] <- df_pred[, 'pred_t720'] <- df_pred[, 'pred_t1080'] <- NA
score_out_mat <- array(NA, dim = c(length(rand_id), K_0AGQ, 3))
# dim indexes subject, eigenfunction and max obs time respectively

# nAGQ=5
df_pred2 <- df_est_latent_5AGQ %>% filter(id %in% rand_id)
df_pred2[, 'pred_t360'] <- df_pred2[, 'pred_t720'] <- df_pred2[, 'pred_t1080'] <- NA
score_out_mat2 <- array(NA, dim = c(length(rand_id), K_5AGQ, 3))
```

```{r, warning=FALSE}
# prediction for a single subject
# nAGQ=0
for(i in rand_id){
  df_i <- df %>% filter(id==i) %>% mutate(bin=as.numeric(bin))
  # prediction
  pred_t360 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=360),
                                 fpca_fit = fpca_mod_0AGQ, K = K_0AGQ)
  pred_t720 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=720),
                                 fpca_fit = fpca_mod_0AGQ, K = K_0AGQ)
  pred_t1080 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=1080),
                                  fpca_fit = fpca_mod_0AGQ, K = K_0AGQ)
  # prediction in container
  df_pred[df_pred$id==i, 'pred_t360'] <- pred_t360$eta_pred
  df_pred[df_pred$id==i, 'pred_t720'] <- pred_t720$eta_pred
  df_pred[df_pred$id==i, 'pred_t1080'] <- pred_t1080$eta_pred
  # score in container
  # score_out_mat[i, ,1] <- pred_t360$score_out
  # score_out_mat[i, ,2] <- pred_t720$score_out
  # score_out_mat[i, ,3] <- pred_t1440$score_out
}

@@

```{r, warning=FALSE}
# prediction for a single subject
# nAGQ=5
for(i in rand_id){
  df_i <- df %>% filter(id==i) %>% mutate(bin=as.numeric(bin))
  # prediction
  pred_t360 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=360),
                                 fpca_fit = fpca_mod_5AGQ, K = K_5AGQ)
  pred_t720 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=720),
                                 fpca_fit = fpca_mod_5AGQ, K = K_5AGQ)
  pred_t1080 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=1080),
                                  fpca_fit = fpca_mod_5AGQ, K = K_5AGQ)
  # prediction in container
  df_pred2[df_pred2$id==i, 'pred_t360'] <- pred_t360$eta_pred
  df_pred2[df_pred2$id==i, 'pred_t720'] <- pred_t720$eta_pred
  df_pred2[df_pred2$id==i, 'pred_t1080'] <- pred_t1080$eta_pred
  # score in container
  # score_out_mat[i, ,1] <- pred_t360$score_out
  # score_out_mat[i, ,2] <- pred_t720$score_out
  # score_out_mat[i, ,3] <- pred_t1440$score_out
}

```{r}
df_pred$pred_t360[df_pred$bin<=360] <- NA
df_pred$pred_t720[df_pred$bin<=720] <- NA
df_pred$pred_t1080[df_pred$bin<=1080] <- NA
# df_pred %>% filter(id == rand_id[1])

df_pred2$pred_t360[df_pred2$bin<=360] <- NA
df_pred2$pred_t720[df_pred2$bin<=720] <- NA
df_pred2$pred_t1080[df_pred2$bin<=1080] <- NA
```

```{r, warning=FALSE}
ggarrange(
df_pred %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id,scales = "free")+
  labs(title = "nAGQ=0"),

df_pred2 %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id,scales = "free")+
  labs(title = "nAGQ=5"),

nrow = 1
)
```

@@

```{r, warning=FALSE, message=FALSE}
#PIRLS
df_pred <- df_est_latent_0AGQ %>% filter(id %in% rand_id)
df_pred[, 'pred_t360'] <- df_pred[, 'pred_t720'] <- df_pred[, 'pred_t1080'] <- NA
score_out_mat <- array(NA, dim = c(length(rand_id), K_0AGQ, 3))

# AGQ
df_pred2 <- df_est_latent_5AGQ %>% filter(id %in% rand_id)
df_pred2[, 'pred_t360'] <- df_pred2[, 'pred_t720'] <- df_pred2[, 'pred_t1080'] <- NA
score_out_mat <- array(NA, dim = c(length(rand_id), K_5AGQ, 3))

```{r, results='hide'}
# unique id
# prediction for a single subject
source(here("Code/OutsampBayes.R"))

# PRILS
for(i in rand_id){
  df_i <- df %>% filter(id==i)

  # prediction 
  ## up to 360
  pred_t1 <- out_pred_laplace(fpca_mod_0AGQ, df_i %>% filter(sind<=360))
  eta_pred_t1 <- fpca_mod_0AGQ$mu+fpca_mod_0AGQ$efunctions%*%pred_t1$score_out
  df_pred[df_pred$id == i, 'pred_t360'] <- eta_pred_t1
  ## up to 720
  pred_t2 <- out_pred_laplace(fpca_mod_0AGQ, df_i %>% filter(sind<=720))
  eta_pred_t2 <- fpca_mod_0AGQ$mu+fpca_mod_0AGQ$efunctions%*%pred_t2$score_out
  df_pred[df_pred$id == i, 'pred_t720'] <- eta_pred_t2
  ## up to 1080
  pred_t3 <- out_pred_laplace(fpca_mod_0AGQ, df_i %>% filter(sind<=1080))
  eta_pred_t3 <- fpca_mod_0AGQ$mu+fpca_mod_0AGQ$efunctions%*%pred_t3$score_out
  df_pred[df_pred$id == i, 'pred_t1080'] <- eta_pred_t3

df_pred$pred_t360[df_pred$bin<=360] <- NA
df_pred$pred_t720[df_pred$bin<=720] <- NA
df_pred$pred_t1080[df_pred$bin<=1080] <- NA
```

```{r, results='hide'}
# AGQ
for(i in rand_id){
  df_i <- df %>% filter(id==i)

  # prediction 
  ## up to 360
  pred_t1 <- out_pred_laplace(fpca_mod_5AGQ, df_i %>% filter(sind<=360))
  eta_pred_t1 <- fpca_mod_5AGQ$mu+fpca_mod_5AGQ$efunctions%*%pred_t1$score_out
  df_pred2[df_pred2$id == i, 'pred_t360'] <- eta_pred_t1
  ## up to 720
  pred_t2 <- out_pred_laplace(fpca_mod_5AGQ, df_i %>% filter(sind<=720))
  eta_pred_t2 <- fpca_mod_5AGQ$mu+fpca_mod_5AGQ$efunctions%*%pred_t2$score_out
  df_pred2[df_pred2$id == i, 'pred_t720'] <- eta_pred_t2
  ## up to 1080
  pred_t3 <- out_pred_laplace(fpca_mod_5AGQ, df_i %>% filter(sind<=1080))
  eta_pred_t3 <- fpca_mod_5AGQ$mu+fpca_mod_5AGQ$efunctions%*%pred_t3$score_out
  df_pred2[df_pred2$id == i, 'pred_t1080'] <- eta_pred_t3

df_pred2$pred_t360[df_pred2$bin<=360] <- NA
df_pred2$pred_t720[df_pred2$bin<=720] <- NA
df_pred2$pred_t1080[df_pred2$bin<=1080] <- NA
# df_pred %>% filter(id == rand_id[1])
```

```{r, warning=FALSE}
ggarrange(
df_pred %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id,scales = "free")+
  labs(title = "nAGQ=0"),

df_pred2 %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id,scales = "free")+
  labs(title = "nAGQ=5"), nrow = 1
)
```
